### 2018-01-20 README.Rmd
Update README.Rmd
Update README on GitHub

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer)
[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) 
[![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)

@@

>>>>

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/andrewpbray/infer?branch=master&svg=true)](https://ci.appveyor.com/project/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)

@@

Other examples are available in the package vignettes.

***

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/andrewpbray/infer/blob/master/CONDUCT.md). By participating in this project you agree to abide by its terms.
